\zchapter{Introduction}

% <person>'s welcome
\newenvironment{welcome}[3]
{
	
%	\begin{mdframed}[backgroundcolor=white]
	
\color{black}{\section{#1's Welcome}}
\color{black}{\noindent \bf Incoming message from #2  <\href{mailto:#3@ucc.asn.au}{#3@ucc.asn.au}>:}





}{}



\begin{welcome}{President}{Mitchell Pomery}{bobgeorge33}

\noindent Welcome to the UCC and our Survival Guide!

UCC is a combination of students interested in computers and people in the workplace who have failed to escape our grasp.
Our club is a no knowledge needed place where you can come to meet friends, work on your projects or play games.
You don't need any technical knowledge to enjoy what our club has to offer and the evets we run range in skill level to make sure everyone is catered for.
If you want to learn how to program we have an intro to programming tutorial and if you already know how to, we have frequent hacking nights were you can work on your projects, or maybe help someone with theirs.
We also run a heap of social events such as LANs, our Annual Camp during July, the Charity Vigil and Tech Talks throughout the year.

If you want to keep up to date with whats happening at UCC, you can join our mailing lists or our facebook group.

UCC has always been a social club for students interested in computers who want to meet new friends, work on projects or play games during breaks.
No technical experience is necessary to join up but if you do want to learn more and get involved with computers be sure to attend our many Tech Talks and Hacking Nights announced on our primary mailing list ucc@.
We also host a bunch of social events throughout the year such as LANs, the Quiz Night, our Annual Camp in July and Charity Vigil.
Be sure to attend the Fresher's Welcome and Annual General Meeting to get the best introduction to the club and run for Fresher Rep, a great first step to becoming involved in the UCC Committee.

The UCC Clubroom has been the focal centre of the club for years.
With numerous clubroom desktops, machine room and our famous Coke and Snack Machines it provides everything you could want on a typical university day.
Recently, some new chairs, keyboards and mice have been purchased to improve equipment and an Oculus Rift bought for all members to try out, just ask a door member.

Founded in 1974, the UCC is one of the oldest student run computer clubs in the world, even older than the Computer Science Department here at UWA.
To celebrate, we are hosting a 40th Anniversary Dinner in September where members old and new will gather to learn and reminisce over our rich history.
History which no doubt will be dug up again throughout the year.

So make sure you come to the clubroom, set up your account and enhance your university experience at UCC.

Mitchell Pomery [BG3]
UCC President 2014
\end{welcome}

%\pagebreak

%\begin{welcome}{Zanchey}{David Adam}{zanchey}
%There is no escape! Don't make me destroy you. Fresher, you do not yet realize your importance. You've only begun to discover your power! Join me, and I will complete your training! With our combined strength, we can end this destructive conflict, and bring order to the galaxy.

%Join us, and together we can rule the galaxy, as wheel and fresher. Come with me! It is the only way!

%\end{welcome}


